---
title: "UFO Sightings"
subtitle: ""
author: "???? <br> Du Shi,Kunning Zhang,Wenhui Zhang,Zhaojun Meng,Zhe Xue"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
```

```{r load-data, include = FALSE}
complete <- read_csv("complete.csv")
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```


```{r include=FALSE}
style_xaringan(
  title_slide_background_image = "img/1.jpg"
)
```

class: center, middle

## A statement of the dataset and our research question

For our final project,We will use UFO Sightings Dataset,which was collected by NATIONAL UFO REPORTING CENTER    (NUFORC).It contains 88875 records of reported UFO Sightings from 1906-2014.
   
Our analysis will seek to answer the following questions:
   
1.What shape of UFO was recorded,and what is the most common shape?

2.Which area has the highest frequency of UFO Sightings? 

3.which hemisphere has more UFO sighting appeared?

---
This is the output of our data frame in the slides.
```{r,echo = FALSE}
 glimpse(complete)
```
---

class: inverse, center, middle

##1.The most common shape of UFO

---
We use shape variable to solve this question
```{r,echo = FALSE}
complete%>%
  count(shape)%>%
  arrange(desc(n))


```

We find UFOs have 30 different shapes,they also contain unknown shape,so maybe they have more shapes.

The most common shape is light,it is much more than the triangle.

---

class: inverse, middle, center

#2.The area that has the highest frequency of UFO Sightings

---
In this question, we use variable "country" to find out the country with highest number of UFO Sightings.(The variable "country" with "NA" is named as Other.)

```{r,echo = FALSE}
complete %>%
  mutate(country = 
           case_when(
             country == "au" ~ "Australia",
             country == "ca" ~ "Canada",
             country == "de" ~ "Germany",
             country == "gb" ~ "Great Britain",
             country == "us" ~ "United States of America",
             TRUE ~ "Other"
        )) %>%
  count(country) %>%
  arrange(desc(n)) %>%
  rename(number = n) 
```
We find the United States of America has the highest number of UFO Sightings.
---
We can also use variable "state" and "city" to find the city with highest number of UFO Sightings in US.
```{r recode-country, echo = FALSE}
complete %>%
  mutate(country = 
           case_when(
             country == "au" ~ "Australia",
             country == "ca" ~ "Canada",
             country == "de" ~ "Germany",
             country == "gb" ~ "Great Britain",
             country == "us" ~ "United States of America",
             TRUE ~ "Other"
        )) %>%
  filter(country == "United States of America")%>%
  count(city,state) %>%
  arrange(desc(n)) %>%
  rename(number = n)
```

---

class: inverse, middle, center

#3.The hemisphere that have more UFO seighting


---
In this question, variable "latitude" is used to discuss the question.
We will first look at the sightings happened in equator.

```{r,echo = FALSE}
equator <- filter(complete, latitude== "0")
count(equator, latitude)
```
Then look at the sightings in southernhimisphere

```{r,echo = FALSE}
southernhemisphere <- filter(complete,latitude < "0")
count(southernhemisphere, latitude) %>%
  arrange(desc(n))
```




---
Then look at the sightings in northernhimisphere.
 
```{r,echo = FALSE}
northernhemisphere <- filter(complete, latitude > "0")
count(northernhemisphere, latitude) %>%
  arrange(desc(n))
```
From the data, we can find that it is clear that if UFO sighting is real, then it is more likely to be seen in northernhimisphere.

---


# Plots

```{r recode-species, echo = FALSE}
# In this chunk I'm doing a bunch of analysis that I don't want to present 
# in my slides. But I need the resulting data frame for a plot I want to present.
iris_modified<-iris %>%
  mutate(Species = fct_other(Species, keep = "setosa"))
```

```{r plot-iris, echo = FALSE}
# Code hidden with echo = FALSE
# Uses modified iris dataset from previous chunk
# Play around with height and width until you're happy with the look
ggplot(data = iris_modified, mapping = aes(x = Sepal.Width, y = Sepal.Length, color = Species)) +
  geom_point() + 
  theme_minimal() # theme options: https://ggplot2.tidyverse.org/reference/ggtheme.html
```

---

## Plot and text

.pull-left[
- Some text
- goes here
]
.pull-right[
```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
# see how I changed out.width and fig.width from defaults
# to make the figure bigger
ggplot(penguins, aes(x = bill_length_mm, y = species, color = species)) +
  geom_boxplot() +
  theme_minimal()
```
]

---

# Tables

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r iris-table, echo = FALSE}
kable(head(iris), format = "html")
```

---

# Images

```{r castle, echo = FALSE, out.width = "60%", fig.align = "center", fig.cap = "Image credit: Photo by Jörg Angeli on Unsplash."}
include_graphics("https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80")
```

Or you can also include a full page image. See next slide.

---

background-image: url(https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80)

---

# Math Expressions

You can write LaTeX math expressions inside a pair of dollar signs, e.g. &#36;\alpha+\beta$ renders $\alpha+\beta$. You can use the display style with double dollar signs:

```
$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$
```

$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$

Limitations:

1. The source code of a LaTeX math expression must be in one line, unless it is inside a pair of double dollar signs, in which case the starting `$$` must appear in the very beginning of a line, followed immediately by a non-space character, and the ending `$$` must be at the end of a line, led by a non-space character;

1. There should not be spaces after the opening `$` or before the closing `$`.

1. Math does not work on the title slide (see [#61](https://github.com/yihui/xaringan/issues/61) for a workaround).

---

# Feeling adventurous?

- Want to find out more about `xaringan`? See https://slides.yihui.name/xaringan/#1.

- You are welcomed to use the default styling of the slides. In fact, that's what I expect majority of you will do. You will differentiate yourself with the content of your presentation.

- But some of you might want to play around with slide styling. The 
`xaringanthemer` provides some solutions for this that: https://pkg.garrickadenbuie.com/xaringanthemer.

- And if you want more bells and whistles, there is also `xaringanExtra`: https://pkg.garrickadenbuie.com/xaringanExtra.
